---
title: 'STAT 435: Homework 4'
author: "First Last"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Q1. Question 7 of Chapter 7 of the ISLR book. (Page 299).
The Wage data set contains a number of other features not explored in this chapter, such as marital status (maritl), job class (jobclass), and others. Explore the relationships between some of these other predictors and wage, and use non-linear fitting techniques in order to fit flexible models to the data.

Create plots of the results obtained, and write a summary of your findings.
```{r Q1}
# Code goes here
library(ISLR)
data(Wage)
library(splines)
attach(Wage)
plot(Wage$age, Wage$wage, col="blue")
plot(Wage$maritl, Wage$wage, col="orange")
plot(Wage$jobclass, Wage$wage, col="yellow")

# Married people seem to make more but is this due to marriage or age?
# Explore this

```


### Q2. Question 8 of Chapter 7 of the ISLR book. (Page 299).
Fit some of the non-linear models investigated in this chapter to the Auto data set. Is there evidence for non-linear relationships in this data set? Create some informative plots to justify your answer.
```{r Q2}
# Code goes here

```


### Question 9 of Chapter 7 of the ISLR book. (Page 299).
This question uses the variables dis (the weighted mean of distances to five Boston employment centers) and nox (introgen oxides concentration in parts per 10 million) from the Boston data. We will treat dis as the predictor and nox as the response.
```{r Q3}
# (a) Use the poly() function to fit a cubic polynomial regression to predict nox using dis. Report the regression output, and plot the resulting data and polynomial fits.

#(b) Plot the polynomial fits for a range of different polynomial degrees (say, from 1 to 10), and report the associated residual sum of squares.

#(c) Perform cross-validation or another approach to select the optimal degree for the polynomial, and explain your results.

#(d) Use the bs() function to fit a regression spline to predict nox using dis. Report the output for the fit using four degrees of freedom. How did you choose the knots? Plot the resulting fit.

#(e) Now fit a regression spline for a range of degrees of freedom, and plot the resulting fits and report the resulting RSS. Describe the results obtained.

#(f) Perform cross-validation or anotehr approach in order to select the best degrees of freedom for a regression spline of thuis data. Describe your results.
```


### Question 10 of Chapter 7 of the ISLR book. (Page 300).
This question relates to the College data set.
```{r Q4}
# (a) Split the data into a training set and test set. Using out-of-state tuition as the response and the other variables as the predictors, preform forward stepwise selection on the training set in order to identify a satisfactory model that uses just a subset of the predictors.

#(b) Fit a GAM on the training data, using out-of-state tuition as the response and the features selected in the previous step as the predictors. Plot the results, and explain your feelings.

#(c) Evaluate the model obtained on the test set, and explain the results obtained.

#(d) For which variables, if any, is there evidence of a non-linear relationship with the response?
```
